---
title: "Documentation for the Interactive Projection Tool for COVID-19 Interventions"
author: "C-SPEC"
output: html_fragment
---

<!-- SETUP --> 

```{r setup, include=FALSE}
# These set the global options
knitr::opts_chunk$set(echo=FALSE, out.width='60%', fig.align='center')

# Chunk specific options can still be set in each R code chunks' header
# e.g. ```{r example_code_block, echo=TRUE, out.width='100%', fig.aling='right'}
 
devtools::load_all()
```


<!-- For anybody that needs an introduction to Rmarkdown: 
     https://rmarkdown.rstudio.com/articles_intro.html -->

<!-- Comments are formatted as per this example comment --> 

<!-- $Math equations$ can be wrapped in single dollar-signs for inline math text --> 

<!-- $$Math equations$$ can be wrapped in double dollar-signs for math equations that get 
     centered on their own line--> 

<!-- Rmarkdown is based on markdown, so use markdown syntax to do 
     simple text formatting if needed --> 

<!-- Good guide on how to use markdown: https://guides.github.com/features/mastering-markdown/ --> 

## Model Structure

```{r include_model_diagram}
model_diagram_path <- system.file('documentation/model_diagram/model_diagram.png',
    package='covid.epi')

knitr::include_graphics(model_diagram_path)
```

## Similar Work

See similar projects, such as:

  - C-SPEC's own [COVID-19 Hospital Capacity Model](https://forrestcrawford.shinyapps.io/covid19_icu/) 
  - [COVID-19 Hospital Impact Model for Epidemics (CHIME)](https://penn-chime.phl.io/) 
  - [COVID-19 Scenarios](https://github.com/neherlab/covid19_scenarios)
  - [Epidemic Calculator](http://gabgoh.github.io/COVID/index.html)
  - [Modeling COVID-19 Spread vs Healthcare Capacity](https://alhill.shinyapps.io/COVID19seir/)
  - [Potential Long-Term Intervention Strategies for COVID-19](https://covid-measures.github.io/) 

## About C-SPEC

Please feel free to reach out to us with any questions at <c19spec@gmail.com>

## How can I find out more? 

Learn more about us at our website <https://covid-spec.org>. 

Visit the GitHub repository for this project at <https://github.com/abilinski/COVID19>. 

Read our technical documentation, linked below for download.

